\appendix
%\renewcommand{\thesection}{\Alph{section}}
%\setcounter{section}{0} 
\renewcommand{\thesubsection}{\Alph{subsection}}
\setcounter{subsection}{0} 
%\renewcommand{\thesubsubsection}{\Alph{subsubsection}}
%\setcounter{subsubsection}{0} 
\renewcommand{\thetable}{\Alph{table}}
\renewcommand{\thefigure}{\Alph{figure}}
\setcounter{table}{0} 
\section*{Appendix}
%\fancyhead{} % remove the header in the appendix

\begin{thebibliography}{10}
	
\bibitem{Bach2022}	
Bach, P., Chernozhukov, V., Kurz, M. S., and Spindler, M., 
\textit{DoubleML - An Object-Oriented Implementation of Double Machine Learning in Python, Journal of Machine Learning Research}, 23(53): 1-6, 
2022.

\bibitem{Bach2021}
Bach, P., Chernozhukov, V., Kurz, M. S., and Spindler, M., 
\textit{DoubleML - An Object-Oriented Implementation of Double Machine Learning in R}, 
2021.
	
\bibitem{Bell2017}
Belloni, A., Chernozhukov, V., Fernández‐Val, I. and Hansen, C., 
\textit{Program Evaluation and Causal Inference With High‐Dimensional Data}, Econometrica, 85: 233-298,
2017.

\bibitem{Cher2015}
Chernozhukov, V., Hansen, C. and Spindler, M., 
\textit{Post-Selection and Post-Regularization Inference in Linear
Models with Many Controls and Instruments},
American Economic Review: Papers and Proceedings, 105 (5): 486-90,
2015.
    
\bibitem{Cher2018}
Chernozhukov V., Chetverikov D., Demirer M., Duflo E., Hansen C., Newey W.,  Robins J.,
  \textit{Double/debiased machine learning for treatment and structural parameters},
  The Econometrics Journal, 
   21(1), pp.C1-C68,
  2018.

\bibitem{Farb2020}
Farbmacher, H., Guber, R. and Klaaßen, S.,
\textit{Instrument Validity Tests with Causal Forests}, 
MEA Discussion Paper, 13-2020,
2020.

\bibitem{frisch1933}  
  Frisch R., Waugh F.,
  \textit{Partial Time Regressions as Compared with Individual Trends}, 
  Econometrica, 1 (4), 
  387–401,
  1933. 
  
\bibitem{Lovell1963}  
  Lovell M.,
  \textit{Seasonal Adjustment of Economic Time Series and Multiple Regression Analysis},
   Journal of the American Statistical Association,
    58 (304), 
    993–1010,
    1963.
    .
\bibitem{Lovell2008}  
  Lovell M.,
   \textit{A Simple Proof of the FWL Theorem},
    Journal of Economic Education,
     39 (1), 88–91,
   	2008.
  
  
\bibitem{rob1988}
Robinson P.,  
\textit{Root-N-Consistent Semiparametric
Regression}, 
Econometrica,
 56(4):931-954,
 1988.

\end{thebibliography}

